---
title: "prestate_LMM"
output: html_document
date: '2023-10-10'
---
#load libraries
```{r}
library(dplyr)
library('lme4')
library('lmerTest')
library('arrow')
library('gtsummary')
library('emmeans')
library('effectsize')
library('olsrr')
library('ARTool')
```

#load data from cardiac

```{r}
#df<-read.csv('/Volumes/BBC/BBC/WP1/data/EEG/tsk/ana/prestate/prestate_cardiac_inter.csv')

df_card<-arrow::read_feather('/Volumes/BBC/BBC/WP1/data/EEG/tsk/ana/prestate/param df/wholegfp/cardiac_phase_5_clusters_tsk_n_prestate_wholegfp.feather')



```
filter  according to map 
the index of the map goes from 0-4, they correspond to the conventional topographies
map 0 = D
map 1 = A
map 2 = E
map 3 = C
map 4 = B
```{r}
df_card$map<-factor(df_card$map)
df_card$g_num<-factor(df_card$g_num)
df_card$awareness<-factor(df_card$awareness)
df_card$phy_cond<-factor(df_card$phy_cond)
map_val_card="1"#change this value to get the corresponding map
df_map_card <-df_card %>% filter(map==map_val_card)

```


2 different dv 
timecov_ = timecoverage (% of time in which there's one rather than the other)
gev_ = global explained variance 

```{r}
model_awa_card<-lmer(timecov_~awareness*phy_cond+(1|g_num), data=df_map_card)
summary(model_awa_card)

anova(model_awa_card)
eta_squared(model_awa_card) #partial eta by default
```


```{r}
qqnorm(residuals(model_awa_card))
qqline(resid(model_awa_card))

# Calcola i residui del modello
residui <- resid(model_awa_card)

# Standardizza i residui
residui_std <- (residui - mean(residui)) / sd(residui)

# Test di Kolmogorov-Smirnov contro una distribuzione normale
ks.test(residui_std, "pnorm")

```

non-parametric option (even normality of residuals ok)
```{r}



# Modello ART per una 2x2 ANOVA con soggetto come random effect
mod_art <- art(timecov_~awareness*phy_cond+(1|g_num), data=df_map_card)

# ANOVA sui dati trasformati
anova(mod_art)
```

```{r}
model_awa_card<-lmer(gev_~awareness*phy_cond+(1|g_num), data=df_map_card)
summary(model_awa_card)

anova(model_awa_card)
eta_squared(model_awa_card) #partial eta by default
```

```{r}
qqnorm(residuals(model_awa_card))
qqline(resid(model_awa_card))
shapiro.test(resid(model_awa_card))

```
#load data from rsp

```{r}
#df<-read.csv('/Volumes/BBC/BBC/WP1/data/EEG/tsk/ana/prestate/prestate_cardiac_inter.csv')

df_rsp<-arrow::read_feather('/Volumes/BBC/BBC/WP1/data/EEG/tsk/ana/prestate/param df/wholegfp/rsp_phase_5_clusters_tsk_n_prestate_wholegfp.feather')



```
filter  according to map 
the index of the map goes from 0-4, they correspond to the conventional topographies
map 0 = D
map 1 = A
map 2 = E
map 3 = C
map 4 = B
```{r}
df_rsp$map<-factor(df_rsp$map)
df_rsp$g_num<-factor(df_rsp$g_num)
df_rsp$awareness<-factor(df_rsp$awareness)
df_rsp$phy_cond<-factor(df_rsp$phy_cond)
map_val_rsp="0" #change this value to get the corresponding map
df_map_rsp <-df_rsp %>% filter(map==map_val_rsp)

```


2 different dv 
timecov_ = timecoverage (% of time in which there's one rather than the other)
gev_ = global explained variance 

```{r}
model_awa_rsp<-lmer(timecov_~awareness*phy_cond+(1|g_num), data=df_map_rsp)
summary(model_awa_rsp)

anova(model_awa_rsp)
eta_squared(model_awa_rsp) #partial eta by default
```


```{r}
model_awa_rsp<-lmer(gev_~awareness*phy_cond+(1|g_num), data=df_map_rsp)
summary(model_awa_rsp)

anova(model_awa_rsp)
eta_squared(model_awa_rsp) #partial eta by default
```

```{r}
qqnorm(residuals(model_awa_rsp))
qqline(resid(model_awa_rsp))
# Calcola i residui del modello
residui <- resid(model_awa_card)

# Standardizza i residui
residui_std <- (residui - mean(residui)) / sd(residui)

# Test di Kolmogorov-Smirnov contro una distribuzione normale
ks.test(residui_std, "pnorm")


```

